---
title: "Curriculum Vitae"
format:
    html:
        toc: true
        page-layout: full
        include-after-body: 
            text: |
                <script src="../assets/aos.js"></script>
                <script>
                AOS.init({
                anchorPlacement: 'top-left',
                duration: 1000,
                offset: 120
                });
                </script>
    pdf:
        include-in-header: columns.tex
        geometry:
            - top=20mm
            - left=20mm
            - right=20mm
            - bottom=20mm
css: ../assets/cv.css
format-links: [pdf]
---

```{=html}
<style>
.flushright {
   text-align: right;
   display: inline-block;
   width: 25% !important;
}

.col {
    width: 100%;
}

.rightcol {
    width: 100%;
}

.whitecol {
    width: 1% !important;
}

.cols {display: flex;}
</style>
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: load-libraries

library(httr2)
library(tibble)
library(stringr)
library(textutils)
```

::: {.print-only .contact-block}
Piyadi Gamage Jayani Lakshika\
Department of Econometrics and Business Statistics\
Monash University, Australia

Email: jayani.piyadigamage\@monash.edu, jayanilakshika76\@gmail.com\
Website: https://jayanilakshika.netlify.app/\
GitHub: https://github.com/JayaniLakshika\
LinkedIn: https://www.linkedin.com/in/jayani-lakshika-9a0297162
:::


:::{data-aos="fade-up" data-aos-duration="2000" data-aos-anchor-placement="center-bottom"}

<!-- ```{=html} -->
<!-- <script src="https://code.jquery.com/jquery-3.7.1.slim.min.js" integrity="sha256-kmHvs0B+OpCW5GVHUNjv9rOmY0IvSIRcf7zGUDTDQM8=" crossorigin="anonymous"></script> -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #| echo: false -->
<!-- aos::use_aos() -->
<!-- ``` -->

## {{<fa graduation-cap>}} Education

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**PhD candidate - Statistics**\
Faculty of Business & Economics, Monash University, Australia\
Thesis title: Interactive and Dynamic Graphics for Studying Non-linear Dimension Reduction Models of High-dimensional Data
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
July 2022 --- 
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**B.Sc. (Honours) in Statistics**\
University of Sri Jayewardenepura (USJ), Sri Lanka\
Thesis title: Computer Vision System For Automated Medicinal Plant Identification
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
January 2017 --- December 2020
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Diploma in Computer System Design (DCSD)**\
National Institute of Business Management (NIBM), Sri Lanka\
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
March 2016 --- March 2017
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Certificate in Business Accounting**\
Chartered Institute of Management Accountants (CIMA), Sri Lanka\
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
December 2015 --- September 2016
:::
:::

## {{<fa briefcase>}} Appointments Held

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Teaching Associate**\
Department of Econometrics and Business Statistics, Monash University, Australia
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
January 2023 --- 
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Teaching Assistant (Temporary Instructor)**\
University of Sri Jayewardenepura (USJ), Sri Lanka
:::
::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
July 2021 --- July 2022
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Associate Data Analyst**\
Vizuamatix (Pvt) Ltd, Sri Lanka
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
January --- November 2021
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Trainee Data Analyst**\
Vizuamatix (Pvt) Ltd, Sri Lanka
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
July---December 2020
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Research Internship**\
Vizuamatix (Pvt) Ltd, Sri Lanka\
Industrial training as a fulfillment of the degree B.Sc. (Honours) in Statistics
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
January --- June 2020
:::
:::

:::


## {{<fa book>}} Publications

### Papers

Lakshika, J. P., \& Talagala, T. S. (2021). Computer-aided Interpretable Features for Leaf Image Classification. arXiv preprint [arXiv:2106.08077](https://arxiv.org/abs/2106.08077)

### Conference proceedings

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
Young Scientists’ Conference on Multidisciplinary Research (YCMR) abstract publication [(ISSN 2815-0260)](https://drive.google.com/file/d/1-IjgZa75zDf97-PA4Gmj5lsyRUCmE3R5/view?usp=sharing)

:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
October 2021 
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
$17^{th}$ applied science research poster and abstract publication [(Page 74)](https://akastrin.si/as-book-2021-prelim.pdf)
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
September 2021 
:::
:::

```{r}
#| echo: false
#| results: asis
#| eval: false


req <- request("https://api.zotero.org") |>
    req_url_query(
        v = 3,
        include = "bib",
        sort = "date",
        style = "journal-of-ecology",
        itemType = "journalArticle"
    ) |>
        req_headers(`Zotero-API-Key` = Sys.getenv("ZOTERO_API_KEY")) |>
    req_url_path("users", "3027577", "publications", "items") |>
    req_retry()

resp <- req |> 
    req_perform()

a <- resp |> 
    resp_body_json() |> 
    purrr::map("bib") |> 
    unlist() |>
    #convert from HTML
    HTMLdecode() |> 
    # Convert html to markdown
    str_remove_all("<div[^>]*>") |>
    str_remove_all("<\\/div>") |> 
    #replace itallics
    str_replace_all("<\\/?i>", "*") |>
    #remove line breaks???
    str_remove_all("\\n") |>
    # Bold my name 
    str_replace("(Lydeamore, M\\.( J\\.)?)", '**\\1**') |>
    str_trim()

cat(paste0("- ", a), sep="\n")
```

<!-- ## {{<fa money-bill>}} Funding -->

<!-- Almost all of this funding was obtained in partnership with large, collaborative teams. -->

```{r}
#| echo: false
#| message: false
#| eval: false

funding <- tribble(
    ~title, ~organisation, ~amount, ~year,
    "Modelling Work in Low and Middle Income Counties in the Western Pacific Region for the COVID-19 SAGE Working Group", "World Health Organisation", 8157, 2024,
    "Modelling To Support Australia’s Resilience to and Preparedness for Omicron And Future Sars-Cov-2 Variants", "Commonwealth Government of Australia", 80059, 2024,
    "Contractual Partner to Conduct Research on Healthcare-Associated Infection Rates in Phillippine Hospitals", "World Health Organisation Phillippines", 72078, 2023,
    "Centre of Western Public Health Unit", "Contract Research", 25000, 2023,
    "Extending and comparing methods for projecting social contact matrices", "SPECTRUM/SPARK Seed Funding", 19438, 2022,
    "Quantifying longitudinal relationships between community mobility and COVID-19 case incidence in west metropolitan Melbourne", "SPECTRUM/SPARK Seed Funding", 19896, 2022,
    "Modelling to support Australia's national plan for COVID-19", "Commonwealth Government of Australia", 147536, 2021,
    "Modelling to support Australia's transition to 'COVID-normal'", "Australian Office of Health Protection", 25620, 2021
)

format_funding <- function(funded) {
    paste(
        ':::: {.cols data-latex=""}',
        '::: {.col data-latex="{0.85\\textwidth}"}',
        paste0('**',funded$title,'**  '),
        paste0(funded$organisation,'  '),
        paste0('Awarded value: $', scales::comma(funded$amount)),
        ':::',
        '::: {.rightcol .flushright data-latex="{0.15\\textwidth}" }',
        funded$year,
        ':::',
        '::::',
        sep = "\n"
    )
}

```

```{r}
#| echo: false
#| results: asis
#| eval: false

formatted <- lapply(1:nrow(funding), function(i) {
    format_funding(funding[i,])
}) |> unlist()

cat(paste0(formatted), sep = "\n")
```

## <i class="bi bi-chat-quote"></i> Conference presentations and contributed talks

```{r}
#| echo: false

presentations <- tribble(
    ~title, ~extra, ~event, ~year,
    "Visualise your fitted non-linear reduction model in high-dimensional space", NA, "UseR! 2024, Salzburg, Austria", 2024,
    "Visualising how non-linear dimension reduction warps your data", NA, "Faculty of BusEco Three Minute Thesis (3MT) competition, Monash University, Australia", 2024,
    "Visualise your fitted non-linear dimension reduction model in the high-dimensional data space", NA, "Victorian branch of the Australian and New Zealand Industrial and Applied Mathematics
Society (VicANZIAM) 2024 (RMIT university, Melbourne, Australia)", 2024,
"Visualize your fitted non-linear dimension reduction model in the high-dimensional data space", "Invited speaker", "Bioinformatics Seminar, Monash University, Australia", 2024,
"With non-linear dimension reduction, when can you believe what you see?", NA, "Australian Statistical Conference (ASC 2023) (Wollongon, Australia)", 2023,
"Viewing the model from a non-linear dimension reduction in the high-dimensional data space", "Invited speaker", "12th-Conference of the Asian Regional Section of the International
Association for Statistical Computing (IASC-ARS 2023) (Wollongon, Australia)", 2023,
"Higher studies webinar", "Invited speaker", "University of Sri Jayewardenepura (USJ), Sri Lanka", 2023,
"Computer Vision System for Automated Medicinal Plant Identification", "Invited speaker", "NUMBATs meeting, Monash University, Australia", 2022,
"Computer Vision System for Automated Medicinal Plant Identification", "Invited speaker", "Estadistica 2021, the Annual Statistics Day organized by the Statistics Society of University of Sri Jayewardenepura, Sri Lanka", 2021,
"Computer Vision System for Automated Medicinal Plant Identification", "Invited speaker", "Vx Tech Talk 2021, Vizuamatix Pvt. Ltd, Sri lanka", 2021,
"Statistical machine learning for medicinal plant leaves classification", "[Presentation](https://www.youtube.com/watch?v=BSs_vXKRnxE)", "17th Applied Statistics Conference, Solvenia", 2021,
"Statistical machine learning for medicinal plant leaves classification", "[Speed-talk](https://www.youtube.com/watch?v=mfP2LUbj0ig)", "Young Scientists' Conference on Multidisciplinary Research (YSCMR 2021) which is organised by the Young Scientists' Association of the National Institute of Fundamental Studies,
Sri Lanka (NIFS-YSA)", 2021
)

format_presentation <- function(presentation) {
    manipped_title <- ifelse(
        is.na(presentation$extra), 
        paste0('**',presentation$title,'**'),
        paste0('**',presentation$title,'**', " --- ", presentation$extra)
    )
    paste(
        ':::: {.cols data-latex=""}',
        '::: {.col data-latex="{0.85\\textwidth}"}',
        paste0(manipped_title,'  '),
        paste0(presentation$event,'  '),
        ':::',
        '::: {.rightcol .flushright data-latex="{0.15\\textwidth}" }',
        presentation$year,
        ':::',
        '::::',
        sep = "\n"
    )
}

```

```{r}
#| echo: false
#| results: asis

formatted <- lapply(1:nrow(presentations), function(i) {
    format_presentation(presentations[i,])
}) |> unlist()

cat(paste0(formatted), sep = "\n")
```

## {{<fa eye>}} Visiting

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**A/Prof. Ursula Laa**\
At the University of Natural Resources and Life Sciences, Vienna (BOKU University), accompanied by Prof. Di Cook, Prof. Eun-Kyung Lee, and A/Prof. Natalia da Silva (one week)
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
July 2024
:::

:::

## {{<fa cube>}} R packages

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**airpurifyr**: Provide an interface to scrape air quality data from \url{https://openaq.org/}
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**cardinalR**: Collection of data structures.
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**quollr**: Tool to visualise how non-linear dimension reduction warps your data
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**olympics**: Provide an interface to scrape Olympic data from \url{https://olympics.com/}
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**MedLEA**: Software which contains information about medicinal plants in Sri Lanka
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**DSjobtracker**: Software which contains what skills and qualifications are required for data science related jobs
:::
:::

## {{<fa school>}} Teaching

### Tutor

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[ETC5510\] **Introduction to data analysis**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2024
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[ETC1010\] **Introduction to data analysis**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2024
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[ETC3250\] **Introduction to machine learning**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2023 --- 2024
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[ETC5250\] **Introduction to machine learning**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2023 --- 2024
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[ETC5521\] **Exploratory data analysis**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2023
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[STA 326 2.0\] **R Programming**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2022
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[STA 213 2.0\] **Inferential Statistics**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2022
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[STA 214 1.0\] **Nonparametric Statistics**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2022
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[STA 215 2.0\] **Sampling techniques**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2022
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[STA 115 1.0\] **Elements of Sampling**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2022
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[STA 113 2.0\] **Descriptive Statistics**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2022
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[STA 114 2.0\] **Probability and Distribution Theory I**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2022
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[STA 224 2.0\] **Regression Analysis**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2021
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[STA 225 2.0\] **Design of Experiments**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2021
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[STA 226 1.0\] **Data Analysis II**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2021
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[STA 123 2.0\] **Probability and Distribution Theory II**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2021
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[STA 124 2.0\] **Data Analysis I**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2021
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
\[STA 125 1.0\] **Statistical Communication**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2021
:::
:::

## {{<fa award>}} Awards

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Monash Business School Prestigious International Conference Award**\
Monash University, Australia
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2024
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Co-Funded Graduate Research Scholarship, Monash Business School**\
Monash University, Australia
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2022 --- 2026
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Diploma in Computer System Design (DCSD)** --- Gold medalist\
National Institute of Business Management (NIBM), Sri Lanka
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2017
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**OCTAVE competition** --- Finalists\
Research abstract competition organized by OCTAVE company, Sri Lanka
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2021
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Stat Circle quiz competition** --- Winners\
Team member of the winners at inter university quiz competition organized by the Stat Circle Faculty of Science, University of Colombo, Sri Lanka
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2018
:::
:::

## {{<fa comments>}} Academic Service & Community Engagment

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**UseR! 2024 Session Chair**\
Conference in Salzburg, Austria
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2024 
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**ASC Session Chair**\
Australian Statistical Conference in Wollongong, Australia
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2023 
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**WOMBAT tutorials** --- Helper\
Monash University, Australia
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2022 
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Statistical Consultancy Service** --- Department representative\
University of Sri Jayewardenepura (USJ), Sri Lanka
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2020 
:::
:::

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **SPECTRUM Annual Meeting** Organising committee -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2024 -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **SPARK Short Course in Mathematical Diseases Modelling** --- OUCRU\ -->
<!-- Facilitator -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2023 -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **Maths in Industry Study Group** --- NSW Health\ -->
<!-- Moderator -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2023 -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **WOMBAT Communicating with Data Workshop**\ -->
<!-- Organising Committee -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2023 -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **Australian and New Zealand Industrial and Applied Mathematics Executive Committee**\ -->
<!-- Treasurer -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2022-- -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **Australian and New Zealand Industrial and Applied Mathematics Executive Committee**\ -->
<!-- Early Career Representative -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2021--2022 -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **SPECTRUM-SPARK Early Career Researcher Committee**\ -->
<!-- Chair -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2022-- -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **SPARK Short Course in Mathematical Diseases Modelling** -- Mahidol University\ -->
<!-- Facilitator -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2022 -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **Research Tools Workshop in R**\ -->
<!-- Facilitator -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2022 -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **Mathematical Biology Special Interest Group**\ -->
<!-- Treasurer -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2019--2022 -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **ANZIAM 2021 Conference**\ -->
<!-- Organising Committee (Treasurer) -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2020--2021 -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **Computational Biology Research Initiative** -- The University of Melbourne\ -->
<!-- Postgraduate Representative -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2017 -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **Computational Biology Postgraduate Sports Group** -- The University of Melbourne\ -->
<!-- Secretary -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2017--2018 -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **Maths in Industry Study Group**\ -->
<!-- Participant -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2017, 2018, 2019 -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **The ConocoPhilips Science Experience** -- The University of Melbourne\ -->
<!-- Activity Organiser -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2016--2018 -->
<!-- ::: -->
<!-- ::: -->

<!-- ::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.85\\textwidth}"} -->
<!-- **Mathematicians in Schools** -- CSIRO\ -->
<!-- Project Supervisor/Mentor -->
<!-- ::: -->

<!-- ::: {.rightcol .flushright data-latex="{0.15\\textwidth}"} -->
<!-- 2016--2018 -->
<!-- ::: -->
<!-- ::: -->

<!-- **Reviewer**\ -->
<!-- PLoS Comptuational Biology; Scientific Reports; Journal of Applied Mathematics; Journal of Statistical Software; Epidemiology & Infection; Mathematics; Medial Journal of Australia; International Tropical Health; Journal of Antimicrobial Resistance; The R Journal -->

## {{<fa users>}} Professional Memberships

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Statistical Society of Australias (SSA)**\
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2022--
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**R-Ladies Melbourne**
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2022--
:::
:::

::: {.cols data-latex=""}
::: {.col data-latex="{0.85\\textwidth}"}
**Statistics society**\
University of Sri Jayewardenepura (USJ), Sri Lanka
:::

::: {.rightcol .flushright data-latex="{0.15\\textwidth}"}
2017--2022
:::
:::
